### 2024-03-26 thesis/sections/6.1-object-identification.tex
results
results reference resolution game

\begin{table}[ht]
    \centering
    \begin{tabular}{cccc|c}
        \toprule
               &        &     &       & \multicolumn{1}{c}{\textbf{Dale-2}} \\  \cmidrule(lr){5-5}
        $h_r$  & $h_s$  & $n$ & $|V|$ & \textbf{Accuracy}                   \\\midrule
        {100}  & {100}  & {2} & {10}  & {99,96\%}                           \\
        {100}  & {1000} & {2} & {10}  & {99,96\%}                           \\
        {1000} & {100}  & {3} & {10}  & {99,87\%}                           \\
        {500}  & {100}  & {3} & {100} & {99,83\%}                           \\
        {100}  & {100}  & {6} & {50}  & {99,83\%}                           \\
        {100}  & {500}  & {3} & {16}  & {99,7\%}                            \\
        {1000} & {100}  & {6} & {16}  & {99,61\%}                           \\
        {100}  & {100}  & {6} & {100} & {99,57\%}                           \\
        {100}  & {500}  & {1} & {100} & {99,52\%}                           \\
        {100}  & {100}  & {1} & {50}  & {99,35\%}                           \\
        {500}  & {100}  & {1} & {2}   & {99,26\%}                           \\
        {100}  & {500}  & {1} & {50}  & {99,26\%}                           \\
        {500}  & {500}  & {1} & {100} & {99,26\%}                           \\
        {100}  & {500}  & {3} & {100} & {99,83\%}                           \\
        {500}  & {1000} & {1} & {16}  & {98\%}                              \\
        {100}  & {500}  & {1} & {10}  & {96,61\%}                           \\
        {100}  & {1000} & {1} & {100} & {99,44\%}                           \\
        {500}  & {500}  & {6} & {2}   & {95,92\%}                           \\
        {100}  & {1000} & {4} & {2}   & {94,88\%}                           \\
        {100}  & {1000} & {6} & {10}  & {63,15\%}                           \\
        {1000} & {500}  & {2} & {2}   & {62,98\%}                           \\\midrule
        {-}    & {-}    & {-} & {-}   & {62,72\% (baseline)}                \\\midrule
        {100}  & {1000} & {3} & {2}   & {61,2\%}                            \\
        \bottomrule
    \end{tabular}
    \caption{Selected results of the object identification games on the Dale-2 dataset with $e_s=100$ and $e_r=500$}
    \label{tab:results_discriminator_dale-2}
\end{table}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cccc|c}
        \toprule
               &        &     &       & \multicolumn{1}{c}{\textbf{Dale-5}} \\  \cmidrule(lr){5-5}
        $h_r$  & $h_s$  & $n$ & $|V|$ & \textbf{Accuracy}                   \\\midrule
        {1000} & {500}  & {3} & {50}  & {91,75\%}                           \\
        {100}  & {100}  & {6} & {10}  & {91,02\%}                           \\
        {100}  & {100}  & {3} & {10}  & {90,76\%}                           \\
        {100}  & {100}  & {4} & {16}  & {89,76\%}                           \\
        {100}  & {100}  & {2} & {10}  & {88,85\%}                           \\
        {500}  & {1000} & {1} & {100} & {87,11\%}                           \\
        {1000} & {1000} & {6} & {50}  & {85,07\%}                           \\
        {500}  & {1000} & {1} & {10}  & {84,46\%}                           \\
        {500}  & {500}  & {1} & {50}  & {83,29\%}                           \\
        {100}  & {100}  & {1} & {10}  & {80,86\%}                           \\
        {500}  & {100}  & {1} & {100} & {76,74\%}                           \\
        {500}  & {500}  & {4} & {2}   & {77,78\%}                           \\
        {1000} & {1000} & {3} & {2}   & {75,78\%}                           \\
        {100}  & {100}  & {3} & {2}   & {74\%}                              \\
        {500}  & {500}  & {1} & {2}   & {63,41\%}                           \\
        {500}  & {1000} & {2} & {100} & {34,98\%}                           \\
        {500}  & {500}  & {3} & {16}  & {34,77\%}                           \\
        {500}  & {500}  & {6} & {2}   & {34,38\%}                           \\
        {1000} & {1000} & {4} & {2}   & {35,33\%}                           \\
        {1000} & {1000} & {6} & {100} & {35,24\%}                           \\
        \bottomrule
    \end{tabular}
    \caption{Selected results of the object identification games on the Dale-5 dataset with $e_s=100$ and $e_r=500$}
    \label{tab:results_discriminator_dale-5}
\end{table}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cccc|c}
        \toprule
               &        &     &       & \multicolumn{1}{c}{\textbf{CLEVR color}} \\  \cmidrule(lr){5-5}
        $h\_r$ & $h\_s$ & $n$ & $|V|$ & \textbf{Accuracy}                        \\\midrule
        {100}  & {1000} & {3} & {10}  & {73,65\%}                                \\
        {100}  & {1000} & {3} & {16}  & {73,57\%}                                \\
        {500}  & {500}  & {4} & {10}  & {73,57\%}                                \\
        {100}  & {500}  & {3} & {16}  & {70,75\%}                                \\
        {100}  & {1000} & {4} & {50}  & {69,31\%}                                \\
        {1000} & {500}  & {1} & {16}  & {62,85\%}                                \\
        {100}  & {500}  & {1} & {10}  & {57,12\%}                                \\
        {1000} & {500}  & {6} & {16}  & {54,69\%}                                \\
        {100}  & {100}  & {4} & {2}   & {52,95\%}                                \\
        {1000} & {500}  & {1} & {100} & {52,82\%}                                \\
        {100}  & {1000} & {1} & {100} & {52,34\%}                                \\
        {100}  & {500}  & {3} & {2}   & {51,48\%}                                \\
        {500}  & {1000} & {3} & {16}  & {24,61\%}                                \\
        {100}  & {1000} & {3} & {50}  & {24,48\%}                                \\
        {1000} & {1000} & {4} & {100} & {24\%}                                   \\
        {500}  & {1000} & {1} & {2}   & {23,96\%}                                \\
        {1000} & {100}  & {6} & {10}  & {23,87\%}                                \\
        {500}  & {1000} & {6} & {50}  & {23,87\%}                                \\
        {500}  & {500}  & {2} & {2}   & {22,35\%}                                \\
        \bottomrule
    \end{tabular}
    \caption{Selected results of the object identification games on the CLEVR color dataset with $e_s=100$ and $e_r=500$}
    \label{tab:results_discriminator_color}
\end{table}

>>>>

\begin{table}[ht]
    \centering
    \begin{tabular}{cccc|c}
        \toprule
                                      &           &     &       & \multicolumn{1}{c}{\textbf{Dale-2}} \\  \cmidrule(lr){5-5}
        $h_r$                         & $h_s$     & $n$ & $|V|$ & \textbf{Accuracy}                   \\\midrule
        {100}                         & {100}     & {2} & {10}  & {99,96\%}                           \\
        {100}                         & {1000}    & {2} & {10}  & {99,96\%}                           \\
        {1000}                        & {100}     & {3} & {10}  & {99,87\%}                           \\
        {500}                         & {100}     & {3} & {100} & {99,83\%}                           \\
        {100}                         & {100}     & {6} & {50}  & {99,83\%}                           \\
        {100}                         & {500}     & {3} & {16}  & {99,7\%}                            \\
        {1000}                        & {100}     & {6} & {16}  & {99,61\%}                           \\
        {100}                         & {100}     & {6} & {100} & {99,57\%}                           \\
        {100}                         & {500}     & {1} & {100} & {99,52\%}                           \\
        {100}                         & {100}     & {1} & {50}  & {99,35\%}                           \\
        {500}                         & {100}     & {1} & {2}   & {99,26\%}                           \\
        {100}                         & {500}     & {1} & {50}  & {99,26\%}                           \\
        {500}                         & {500}     & {1} & {100} & {99,26\%}                           \\
        {100}                         & {500}     & {3} & {100} & {99,83\%}                           \\
        {500}                         & {1000}    & {1} & {16}  & {98\%}                              \\
        {100}                         & {500}     & {1} & {10}  & {96,61\%}                           \\
        {100}                         & {1000}    & {1} & {100} & {99,44\%}                           \\
        {500}                         & {500}     & {6} & {2}   & {95,92\%}                           \\
        {100}                         & {1000}    & {4} & {2}   & {94,88\%}                           \\
        {100}                         & {1000}    & {6} & {10}  & \textcolor{purple}{63,15\%}         \\
        {1000}                        & {500}     & {2} & {2}   & \textcolor{purple}{62,98\%}         \\\midrule
        \multicolumn{4}{c|}{baseline} & {62,72\%}                                                     \\\midrule
        {100}                         & {1000}    & {3} & {2}   & \textcolor{purple}{61,2\%}          \\
        \bottomrule
    \end{tabular}
    \caption{Selected results of the object identification games on the Dale-2 dataset with $e_s=100$ and $e_r=500$}
    \label{tab:results_discriminator_dale-2}
\end{table}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cccc|c}
        \toprule
                                      &           &     &       & \multicolumn{1}{c}{\textbf{Dale-5}} \\  \cmidrule(lr){5-5}
        $h_r$                         & $h_s$     & $n$ & $|V|$ & \textbf{Accuracy}                   \\\midrule
        {1000}                        & {500}     & {3} & {50}  & {91,75\%}                           \\
        {100}                         & {100}     & {6} & {10}  & {91,02\%}                           \\
        {100}                         & {100}     & {3} & {10}  & {90,76\%}                           \\
        {100}                         & {100}     & {4} & {16}  & {89,76\%}                           \\
        {100}                         & {100}     & {2} & {10}  & {88,85\%}                           \\
        {500}                         & {1000}    & {1} & {100} & {87,11\%}                           \\
        {1000}                        & {1000}    & {6} & {50}  & {85,07\%}                           \\
        {500}                         & {1000}    & {1} & {10}  & {84,46\%}                           \\
        {500}                         & {500}     & {1} & {50}  & {83,29\%}                           \\
        {100}                         & {100}     & {1} & {10}  & {80,86\%}                           \\
        {500}                         & {100}     & {1} & {100} & {76,74\%}                           \\
        {500}                         & {500}     & {4} & {2}   & {77,78\%}                           \\
        {1000}                        & {1000}    & {3} & {2}   & {75,78\%}                           \\
        {100}                         & {100}     & {3} & {2}   & {74\%}                              \\
        {500}                         & {500}     & {1} & {2}   & {63,41\%}                           \\\midrule
        \multicolumn{4}{c|}{baseline} & {35,07\%}                                                     \\\midrule
        {500}                         & {1000}    & {2} & {100} & \textcolor{purple}{34,98\%}         \\
        {500}                         & {500}     & {3} & {16}  & \textcolor{purple}{34,77\%}         \\
        {500}                         & {500}     & {6} & {2}   & \textcolor{purple}{34,38\%}         \\
        {1000}                        & {1000}    & {4} & {2}   & \textcolor{purple}{35,33\%}         \\
        {1000}                        & {1000}    & {6} & {100} & \textcolor{purple}{35,24\%}         \\
        \bottomrule
    \end{tabular}
    \caption{Selected results of the object identification games on the Dale-5 dataset with $e_s=100$ and $e_r=500$}
    \label{tab:results_discriminator_dale-5}
\end{table}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cccc|c}
        \toprule
                                      &           &     &       & \multicolumn{1}{c}{\textbf{CLEVR color}} \\  \cmidrule(lr){5-5}
        $h\_r$                        & $h\_s$    & $n$ & $|V|$ & \textbf{Accuracy}                        \\\midrule
        {100}                         & {1000}    & {3} & {10}  & {73,65\%}                                \\
        {100}                         & {1000}    & {3} & {16}  & {73,57\%}                                \\
        {500}                         & {500}     & {4} & {10}  & {73,57\%}                                \\
        {100}                         & {500}     & {3} & {16}  & {70,75\%}                                \\
        {100}                         & {1000}    & {4} & {50}  & {69,31\%}                                \\
        {1000}                        & {500}     & {1} & {16}  & {62,85\%}                                \\
        {100}                         & {500}     & {1} & {10}  & {57,12\%}                                \\
        {1000}                        & {500}     & {6} & {16}  & {54,69\%}                                \\
        {100}                         & {100}     & {4} & {2}   & {52,95\%}                                \\
        {1000}                        & {500}     & {1} & {100} & {52,82\%}                                \\
        {100}                         & {1000}    & {1} & {100} & {52,34\%}                                \\
        {100}                         & {500}     & {3} & {2}   & {51,48\%}                                \\
        {500}                         & {1000}    & {3} & {16}  & \textcolor{purple}{24,61\%}              \\
        {100}                         & {1000}    & {3} & {50}  & \textcolor{purple}{24,48\%}              \\
        {1000}                        & {1000}    & {4} & {100} & \textcolor{purple}{24\%}                 \\
        {500}                         & {1000}    & {1} & {2}   & \textcolor{purple}{23,96\%}              \\
        {1000}                        & {100}     & {6} & {10}  & \textcolor{purple}{23,87\%}              \\
        {500}                         & {1000}    & {6} & {50}  & \textcolor{purple}{23,87\%}              \\\midrule
        \multicolumn{4}{c|}{baseline} & {23,74\%}                                                          \\\midrule
        {500}                         & {500}     & {2} & {2}   & \textcolor{purple}{22,35\%}              \\
        \bottomrule
    \end{tabular}
    \caption{Selected results of the object identification games on the CLEVR color dataset with $e_s=100$ and $e_r=500$}
    \label{tab:results_discriminator_color}
\end{table}

### 2024-03-26 thesis/sections/6.3-reference-resolution.tex
results reference resolution game

        {1}                           & {2}     & \textcolor{purple}{34,91}           & \textcolor{purple}{34,81\%}         & \textcolor{purple}{40,61}                & {25,48\%}                   & {39,13}                   & {25\%}                      \\
        {1}                           & {10}    & \textcolor{purple}{35,31}           & {40,15\%}                           & \textcolor{purple}{38,73}                & {28,12\%}                   & \textcolor{purple}{44,19} & {20,53\%}                   \\
        {1}                           & {16}    & \textcolor{purple}{35,4}            & {42,93\%}                           & \textcolor{purple}{39,58}                & {26,17\%}                   & {39,64}                   & {24,18\%}                   \\
        {1}                           & {50}    & {32,64}                             & {42,01\%}                           & \textcolor{purple}{38,99}                & {28,52\%}                   & \textcolor{purple}{42,61} & {20,79\%}                   \\
        {1}                           & {100}   & \textcolor{purple}{36,73}           & \textcolor{purple}{31,21\%}         & \textcolor{purple}{40,25}                & {24,91\%}                   & \textcolor{purple}{41,5}  & {21,44\%}                   \\
        {2}                           & {2}     & \textcolor{purple}{33,76}           & {40,67\%}                           & {35,86}                                  & \textcolor{purple}{31,73\%} & \textcolor{purple}{41,79} & {22,14\%}                   \\

@@

        {2}                           & {16}    & {31,19}                             & {46,27\%}                           & \textcolor{purple}{39,38}                & {28,21\%}                   & \textcolor{purple}{41,74} & {22,7\%}                    \\
        {2}                           & {50}    & \textcolor{purple}{33,66}           & {39,28\%}                           & \textcolor{purple}{39,62}                & {25,35\%}                   & \textcolor{purple}{45,63} & \textcolor{purple}{17,93\%} \\
        {2}                           & {100}   & \textcolor{purple}{35,1}            & \textcolor{purple}{34,81\%}         & \textcolor{purple}{39,86}                & {27,3\%}                    & \textcolor{purple}{45,45} & \textcolor{purple}{19,05\%} \\

@@

        {3}                           & {10}    & \textcolor{purple}{33,74}           & {38,89\%}                           & \textcolor{purple}{40,71}                & {26,48\%}                   & \textcolor{purple}{44,53} & \textcolor{purple}{19,01\%} \\

@@

        {3}                           & {50}    & \textcolor{purple}{34,38}           & {38,93\%}                           & \textcolor{purple}{39,52}                & {26,74\%}                   & {38,4}                    & {24,87\%}                   \\
        {3}                           & {100}   & \textcolor{purple}{33,16}           & {40,19\%}                           & \textcolor{purple}{39,75}                & {27,78\%}                   & \textcolor{purple}{41,29} & {21,83\%}                   \\

@@

        {4}                           & {10}    & \textcolor{purple}{35,01}           & {39,97\%}                           & \textcolor{purple}{40,88}                & {26,39\%}                   & \textcolor{purple}{42,33} & {20,44\%}                   \\
        {4}                           & {16}    & \textcolor{purple}{35,59}           & \textcolor{purple}{35,59\%}         & \textcolor{purple}{37,91}                & \textcolor{purple}{31,86\%} & \textcolor{purple}{41,9}  & {20,27\%}                   \\
        {4}                           & {50}    & \textcolor{purple}{34,99}           & {36,68\%}                           & \textcolor{purple}{40,89}                & {23,26\%}                   & \textcolor{purple}{43,77} & \textcolor{purple}{18,36\%} \\

@@

        {6}                           & {10}    & {32,39}                             & {43,53\%}                           & \textcolor{purple}{38,61}                & {28,26\%}                   & {40,84}                   & {21,74\%}                   \\
        {6}                           & {16}    & \textcolor{purple}{34,87}           & \textcolor{purple}{34,38\%}         & \textcolor{purple}{39,03}                & {26,82\%}                   & {40,34}                   & {23,31\%}                   \\
        {6}                           & {50}    & \textcolor{purple}{33,85}           & {37,07\%}                           & \textcolor{purple}{39,39}                & {27,17\%}                   & {40,8}                    & {22,09\%}                   \\
        {6}                           & {100}   & \textcolor{purple}{34,62}           & {40,02\%}                           & \textcolor{purple}{39,46}                & {25,48\%}                   & \textcolor{purple}{42,53} & \textcolor{purple}{18,4\%}  \\

@@

@@

@@

        {2}                           & {10}      & {96,16\%}                           & {80,26\%}                           & \textcolor{purple}{36,53\%}              \\
        {2}                           & {16}      & {95,84\%}                           & {84,03\%}                           & \textcolor{purple}{39,65\%}              \\

@@

        {3}                           & {16}      & {94,59\%}                           & {81,46\%}                           & {67,88\%}                                \\

@@

        {4}                           & {10}      & {96,08\%}                           & \textcolor{purple}{48,03\%}         & {64,31\%}                                \\

@@

        {4}                           & {50}      & {96,24\%}                           & \textcolor{purple}{48,79\%}         & \textcolor{purple}{43,61\%}              \\

@@

        {6}                           & {10}      & \textcolor{purple}{63,46\%}         & {82,12\%}                           & \textcolor{purple}{40,11\%}              \\

>>>>

        {1}                           & {2}     & \textcolor{purple}{34,91}           & \textcolor{purple}{34,81\%}         & \textcolor{purple}{40,61}                & \textcolor{purple}{25,48\%} & {39,13}                   & {25\%}                      \\
        {1}                           & {10}    & \textcolor{purple}{35,31}           & {40,15\%}                           & \textcolor{purple}{38,73}                & \textcolor{purple}{28,12\%} & \textcolor{purple}{44,19} & {20,53\%}                   \\
        {1}                           & {16}    & \textcolor{purple}{35,4}            & {42,93\%}                           & \textcolor{purple}{39,58}                & \textcolor{purple}{26,17\%} & {39,64}                   & {24,18\%}                   \\
        {1}                           & {50}    & {32,64}                             & {42,01\%}                           & \textcolor{purple}{38,99}                & \textcolor{purple}{28,52\%} & \textcolor{purple}{42,61} & {20,79\%}                   \\
        {1}                           & {100}   & \textcolor{purple}{36,73}           & \textcolor{purple}{31,21\%}         & \textcolor{purple}{40,25}                & \textcolor{purple}{24,91\%} & \textcolor{purple}{41,5}  & {21,44\%}                   \\
        {2}                           & {2}     & \textcolor{purple}{33,76}           & {40,67\%}                           & {35,86}                                  & {31,73\%}                   & \textcolor{purple}{41,79} & {22,14\%}                   \\

@@

        {2}                           & {16}    & {31,19}                             & {46,27\%}                           & \textcolor{purple}{39,38}                & \textcolor{purple}{28,21\%} & \textcolor{purple}{41,74} & {22,7\%}                    \\
        {2}                           & {50}    & \textcolor{purple}{33,66}           & {39,28\%}                           & \textcolor{purple}{39,62}                & \textcolor{purple}{25,35\%} & \textcolor{purple}{45,63} & \textcolor{purple}{17,93\%} \\
        {2}                           & {100}   & \textcolor{purple}{35,1}            & \textcolor{purple}{34,81\%}         & \textcolor{purple}{39,86}                & \textcolor{purple}{27,3\%}  & \textcolor{purple}{45,45} & \textcolor{purple}{19,05\%} \\

@@

        {3}                           & {10}    & \textcolor{purple}{33,74}           & {38,89\%}                           & \textcolor{purple}{40,71}                & \textcolor{purple}{26,48\%} & \textcolor{purple}{44,53} & \textcolor{purple}{19,01\%} \\

@@

        {3}                           & {50}    & \textcolor{purple}{34,38}           & {38,93\%}                           & \textcolor{purple}{39,52}                & \textcolor{purple}{26,74\%} & {38,4}                    & {24,87\%}                   \\
        {3}                           & {100}   & \textcolor{purple}{33,16}           & {40,19\%}                           & \textcolor{purple}{39,75}                & \textcolor{purple}{27,78\%} & \textcolor{purple}{41,29} & {21,83\%}                   \\

@@

        {4}                           & {10}    & \textcolor{purple}{35,01}           & {39,97\%}                           & \textcolor{purple}{40,88}                & \textcolor{purple}{26,39\%} & \textcolor{purple}{42,33} & {20,44\%}                   \\
        {4}                           & {16}    & \textcolor{purple}{35,59}           & \textcolor{purple}{35,59\%}         & \textcolor{purple}{37,91}                & {31,86\%}                   & \textcolor{purple}{41,9}  & {20,27\%}                   \\
        {4}                           & {50}    & \textcolor{purple}{34,99}           & {36,68\%}                           & \textcolor{purple}{40,89}                & \textcolor{purple}{23,26\%} & \textcolor{purple}{43,77} & \textcolor{purple}{18,36\%} \\

@@

        {6}                           & {10}    & {32,39}                             & {43,53\%}                           & \textcolor{purple}{38,61}                & \textcolor{purple}{28,26\%} & {40,84}                   & {21,74\%}                   \\
        {6}                           & {16}    & \textcolor{purple}{34,87}           & \textcolor{purple}{34,38\%}         & \textcolor{purple}{39,03}                & \textcolor{purple}{26,82\%} & {40,34}                   & {23,31\%}                   \\
        {6}                           & {50}    & \textcolor{purple}{33,85}           & {37,07\%}                           & \textcolor{purple}{39,39}                & \textcolor{purple}{27,17\%} & {40,8}                    & {22,09\%}                   \\
        {6}                           & {100}   & \textcolor{purple}{34,62}           & {40,02\%}                           & \textcolor{purple}{39,46}                & \textcolor{purple}{25,48\%} & \textcolor{purple}{42,53} & \textcolor{purple}{18,4\%}  \\

@@

    \label{tab:results:coordinate-reference-resolver-game}

@@

Table \ref{tab:results:coordinate-reference-resolver-game} shows the results of the coordinate reference resolver on different datasets.
The baselines show the predictions of the receiver without information of the sender, and correspond to the structural bias in the dataset.
When looking at how the agents fare with each dataset, not much general improvement can be seen.
Most of the configurations don't beat the baseline, independently of the shown dataset.
If they do, they can improve the mean distance of the predicted coordinates to the center of the target object only by 2 to 4 pixels.
In other words, the guesses are still not consistently precise on the target objects and the agents instead learn to point towards the center of the scene, as the single models in Section \ref{sec:referring_expression_generation}.
However, an influence on the accuracy can be identified.
The accuracy evaluates how many of the predictions are on the target object.
An increase in the accuracy with a stable mean distance corresponds shows a behavior where the agents make more correct predictions on the target objects, while the wrong predictions a further away from the target object.
As a conclusion, this can mean, that the agents' predictions, both correct and incorrect are more confident.
This seems to happen on the \emph{Dale-2} dataset.
The mean distance is not improved, but the accuracy reaches in some configurations up to 46,27\%.
This is an increase of around 13\% compared to the baseline.
While this value is still lower than a random guess between the objects in the scene, it shows, that some information is exchanged between the agents.
The meaning of the messages however doesn't seem to correspond to any attribute.

@@

        {2}                           & {10}      & \textbf{96,16\%}                    & {80,26\%}                           & \textcolor{purple}{36,53\%}              \\
        {2}                           & {16}      & {95,84\%}                           & \textbf{84,03\%}                    & \textcolor{purple}{39,65\%}              \\

@@

        {3}                           & {16}      & {94,59\%}                           & \textbf{81,46\%}                    & \textbf{67,88\%}                         \\

@@

        {4}                           & {10}      & \textbf{96,08\%}                    & \textcolor{purple}{48,03\%}         & \textbf{64,31\%}                         \\

@@

        {4}                           & {50}      & \textbf{96,24\%}                    & \textcolor{purple}{48,79\%}         & \textcolor{purple}{43,61\%}              \\

@@

        {6}                           & {10}      & \textcolor{purple}{63,46\%}         & \textbf{82,12\%}                    & \textcolor{purple}{40,11\%}              \\
